The title

### 2023-04-12 doc/multiverse.Rmd
WIP: use tar_map
Could facet_labels, filename go in model_assets instead?

```{r model-diagnostics}
tar_read(model_diagnostics) |> 
  papaja::apa_table(caption = "Model diagnostics", escape = FALSE,
                    longtable = TRUE)
```

@@

moderator_df <- data.frame(
  moderator = c("bmi", "ses", "sex", "weekday", "season", "region", "daylight", "wear_location", "pa_mostactivehr"),
  moderator_formal = c("BMI", "SES", "sex", "weekday", "season", "region", "daylight hours", "wear location", "most active hour"),
  image_path = c("Bmi", "Ses", "Sex", "Weekday_x", "Season", "Region", "Daylight_hours", "Accelerometer_wear_location", "Pa_mostactivehr")
)

lapply(seq_len(nrow(moderator_df)), function(r){

  moderator <- moderator_df$moderator[r]
  moderator_fig <- gsub("_","-",moderator)
  moderator_formal <- moderator_df$moderator_formal[r]
  image_path <- moderator_df$image_path[r]

  glue::glue(pattern, .open = "_::", .close = "::_")

}) |> paste(collapse = "\n") |> clipr::write_clip()

```

@@

```{r sleep-by-volume-fig-by-wear-location, fig.cap = "Sleep metrics on Physical activity volume by wear location"}
knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Accelerometer_wear_location.jpg"), error = FALSE)
```

@@

```{r sleep-by-intensity-fig-by-wear-location, fig.cap = "Sleep metrics on Physical activity intensity moderated by wear location"}
knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Accelerometer_wear_location.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-duration-fig-by-wear-location, fig.cap = "Physical activity by sleep duration moderated by wear location"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Accelerometer_wear_location.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-wear-location, fig.cap = "Physical activity by sleep efficiency moderated by wear location"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Accelerometer_wear_location.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig-by-wear-location, fig.cap = "Physical activity by sleep onset moderated by wear location"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Accelerometer_wear_location.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-wear-location, fig.cap = "Physical activity by sleep regularity moderated by wear location"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Accelerometer_wear_location.jpg"), error = FALSE)
```
\clearpage

>>>>

```{r model-diagnostics}
tar_read(model_diagnostics) |>
  papaja::apa_table(
    caption = "Model diagnostics", escape = FALSE,
    longtable = TRUE
  )
```

@@

moderator_df <- data.frame(
  moderator = c("bmi", "ses", "sex", "weekday", "season", "region", "daylight", "wear_location", "pa_mostactivehr"),
  moderator_formal = c("BMI", "SES", "sex", "weekday", "season", "region", "daylight hours", "wear location", "most active hour"),
  image_path = c("Bmi", "Ses", "Sex", "Weekday_x", "Season", "Region", "Daylight_hours", "Acc_wear_loc", "Pa_mostactivehr")
)

lapply(seq_len(nrow(moderator_df)), function(r) {
  moderator <- moderator_df$moderator[r]
  moderator_fig <- gsub("_", "-", moderator)
  moderator_formal <- moderator_df$moderator_formal[r]
  image_path <- moderator_df$image_path[r]

  glue::glue(pattern, .open = "_::", .close = "::_")
}) |>
  paste(collapse = "\n") |>
  clipr::write_clip()
```

@@

```{r sleep-by-volume-fig-by-wear-location, fig.cap = "Sleep metrics on Physical activity volume by wear location"}
knitr::include_graphics(here::here("Figures/Sleep on pa_volume by Acc_wear_loc.jpg"), error = FALSE)
```

@@

```{r sleep-by-intensity-fig-by-wear-location, fig.cap = "Sleep metrics on Physical activity intensity moderated by wear location"}
knitr::include_graphics(here::here("Figures/Sleep on pa_intensity by Acc_wear_loc.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-duration-fig-by-wear-location, fig.cap = "Physical activity by sleep duration moderated by wear location"}
knitr::include_graphics(here::here("Figures/Pa on sleep_duration_lag by Acc_wear_loc.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig-by-wear-location, fig.cap = "Physical activity by sleep efficiency moderated by wear location"}
knitr::include_graphics(here::here("Figures/Pa on sleep_efficiency_lag by Acc_wear_loc.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig-by-wear-location, fig.cap = "Physical activity by sleep onset moderated by wear location"}
knitr::include_graphics(here::here("Figures/Pa on sleep_onset_lag by Acc_wear_loc.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig-by-wear-location, fig.cap = "Physical activity by sleep regularity moderated by wear location"}
knitr::include_graphics(here::here("Figures/Pa on sleep_regularity_lag by Acc_wear_loc.jpg"), error = FALSE)
```
\clearpage
